### 2019-01-02 Sections/economics_of_the_quantum_internet.tex
games. structure

@@

@@

\begin{itemize}
	\item \textsc{Isolation}: $X$ and $Y$ build their own systems in isolation, which they utilise independently. There is no cooperation or networking of computational resources between them. This can be considered the status quo ($S$) for the players, as it represents the autarky position and defines the von Neuman \& Morgenstern utility space\index{Utility!Space}.  This is represented in Fig.~\ref{fig:game_theory_1} Importantly, any changes to $X$'s computational capacity has no impact on $Y$'s. So $X$ can take any position along the horizontal axis, and there is no change in $Y$'s utility, and vice versa. The resulting \textit{utility point}\index{Utility!Point}\comment{What's the utility point?} is described here as the intersecting minimum of these options, represented by the point \mbox{$(S_x, S_y)$}.

@@

@@

The first question to ask is, how do mixed strategies\index{Mixed strategies} affect cooperation? To perform this analysis, assume that $X$ has chosen a mixed strategy comprising a combination of \textsc{License} and \textsc{Unify}. In the example shown in Fig.~\ref{fig:game_theory_4}, this results in a utility value of 4 for $X$, represented by the vertical dotted line.

@@

The second question that arises is, what happens to the utility payoff matrix when taxation is imposed?\index{Taxation} The assumption that $X$ and $Y$ are operating in similar regulatory environments can be relaxed. What happens when $X$ is in a more heavily taxed environment than $Y$, or something impacts the utility achieved by the players in an asymmetric manner?

@@

The next question is, what happens with collaboration between players who have different systems? If this assumption is relaxed, what comes of the resulting utility payoff matrix and choice of strategies? The analysis for this assumption had already been presented in the previous discussion. The effective impact of taxation is that it will limit the amount of computational power delivered to market and capture governmental revenue from the sale of compute-time. This is analogous to what happens if $X$ was to build a less powerful system than $Y$. Through collaboration, they could still attain point $Q'$, shown in Fig.~\ref{fig:game_theory_4}, but this time the asymmetry arises as a design consequence rather than a regulatory imposition. Despite $X$ now not contributing as much to the overall computational power of the quantum cloud, choosing the maximising strategy of offering all available computing power to the cloud does maximise individual utility. Furthermore, the subjective nature of the utility derivation means there doesn't have to be a change from the described payoff matrix shown in Fig.~\ref{fig:game_theory_3}. Despite having a less powerful system, the proportional allocation of financial rewards relative to the contribution, means both $X$ and $Y$ could maintain a symmetric utility payoff outcome, like in Fig.~\ref{fig:game_theory_3}. What can be concluded from this analysis is that in a 2-player cooperative game, the player with the more powerful system also has a greater incentive to cooperate\comment{Contradicts earlier conclusion. In my earlier derivations I argued that the leverage phenomena incentivises smaller players more than bigger ones since their leverage is greater. Please clarify or reconcile.}.

This leads to one final question, what happens when the analysis moves beyond just two players? As established previously, the cost and scale limitations associated with quantum computing means there are likely to be limited vendors contributing to the quantum internet. However, it's also likely there will be more than just two. Formulating the $n$-person cooperative game opens up a plethora of possibilities that go beyond the scope of this introductory discussion, but one key takeaway point from the previous analysis is that in general there is a strong motivation for computational cooperation in the quantum world. This then introduces two possible scenarios:

@@

In summary, a game theory approach to understanding the quantum internet shows that there are strong motivations for quantum computing vendors to cooperate in order to globally emaximise net utility. Furthermore, there is a strong potential to affect the possibility of cooperation through market distorting effects such as via the imposition of taxation or regulation. Finally, the two most likely market structures that will develop under the quantum internet are either a natural monopoly\index{Monopoly}, where some form of regulation will be required to ensure economically efficient production, or an oligopoly\index{Oligopoly}, where a few cartels will compete with each other to maximise their productive output. Either way, the quantum marketplace is an extremely interesting and largely unexplored avenue for future research, a new interdisciplinary field sitting at the intersection between economics and quantum information theory. It is also one of great relevance and importance for when this technology becomes a reality.

>>>>

\subsection{Key concepts}

@@

\subsection{Strategies}\index{Strategies}

@@

\begin{itemize}
	\item \textsc{Isolation}: $X$ and $Y$ build their own systems in isolation, which they utilise independently. There is no cooperation or networking of computational resources between them. This can be considered the status quo ($S$) for the players, as it represents the autarky position and defines the von Neuman \& Morgenstern utility space\index{Utility!Space}.  This is represented in Fig.~\ref{fig:game_theory_1}. Importantly, any changes to $X$'s computational capacity has no impact on $Y$'s. So $X$ can take any position along the horizontal axis, and there is no change in $Y$'s utility, and vice versa. The resulting \textit{utility point}\index{Utility!Point}\comment{What's the utility point?} is described here as the intersecting minimum of these options, represented by the point \mbox{$(S_x, S_y)$}.

@@

\subsection{Utility payoff behaviour}

@@

\subsection{Mixed strategies}

How do mixed strategies\index{Mixed strategies} affect cooperation? To perform this analysis, assume that $X$ has chosen a mixed strategy comprising a combination of \textsc{License} and \textsc{Unify}. In the example shown in Fig.~\ref{fig:game_theory_4}, this results in a utility value of 4 for $X$, represented by the vertical dotted line.

@@

\subsection{Taxation}

What happens to the utility payoff matrix when taxation is imposed?\index{Taxation} The assumption that $X$ and $Y$ are operating in similar regulatory environments can be relaxed. What happens when $X$ is in a more heavily taxed environment than $Y$, or something impacts the utility achieved by the players in an asymmetric manner?

@@

\subsection{Resource asymmetry}\index{Resource asymmetry}

What happens with collaboration between players who have different systems? If this assumption is relaxed, what comes of the resulting utility payoff matrix and choice of strategies? The analysis for this assumption had already been presented in the previous discussion. The effective impact of taxation is that it will limit the amount of computational power delivered to market and capture governmental revenue from the sale of compute-time. This is analogous to what happens if $X$ was to build a less powerful system than $Y$. Through collaboration, they could still attain point $Q'$, shown in Fig.~\ref{fig:game_theory_4}, but this time the asymmetry arises as a design consequence rather than a regulatory imposition. Despite $X$ now not contributing as much to the overall computational power of the quantum cloud, choosing the maximising strategy of offering all available computing power to the cloud does maximise individual utility. Furthermore, the subjective nature of the utility derivation means there doesn't have to be a change from the described payoff matrix shown in Fig.~\ref{fig:game_theory_3}. Despite having a less powerful system, the proportional allocation of financial rewards relative to the contribution, means both $X$ and $Y$ could maintain a symmetric utility payoff outcome, like in Fig.~\ref{fig:game_theory_3}. What can be concluded from this analysis is that in a 2-player cooperative game, the player with the more powerful system also has a greater incentive to cooperate\comment{Contradicts earlier conclusion. In my earlier derivations I argued that the leverage phenomena incentivises smaller players more than bigger ones since their leverage is greater. Please clarify or reconcile.}.

\subsection{Multi-player games}

What happens when the analysis moves beyond just two players? As established previously, the cost and scale limitations associated with quantum computing means there are likely to be limited vendors contributing to the quantum internet. However, it's also likely there will be more than just two. Formulating the $n$-person cooperative game opens up a plethora of possibilities that go beyond the scope of this introductory discussion, but one key takeaway point from the previous analysis is that in general there is a strong motivation for computational cooperation in the quantum world. This then introduces two possible scenarios:

@@

\subsection{Conclusions}

In summary, a game theory approach to understanding the quantum internet shows that there are strong motivations for quantum computing vendors to cooperate in order to globally maximise net utility. Furthermore, there is a strong potential to affect the possibility of cooperation through market distorting effects such as via the imposition of taxation or regulation. Finally, the two most likely market structures that will develop under the quantum internet are either a natural monopoly\index{Monopoly}, where some form of regulation will be required to ensure economically efficient production, or an oligopoly\index{Oligopoly}, where a few cartels will compete with each other to maximise their productive output. Either way, the quantum marketplace is an extremely interesting and largely unexplored avenue for future research, a new interdisciplinary field sitting at the intersection between economics and quantum information theory. It is also one of great relevance and importance for when this technology becomes a reality.

\latinquote{Natura nihil frustra facit.}
